### 2024-07-26 conteudo/tool/functionalities.tex
do figures desc

\begin{figure}
\includegraphics[scale=0.5]{explorer_example}
\caption{Explorer Example}
\label{fig:explorer_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{function_example}
\caption{Function Example}
\label{fig:function_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{relatory_example}
\caption{Function Example}
\label{fig:relatory_ex}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.5]{explorer_example}
\caption{Example of the \textit{duplication explorer} functionality of the proposed tool in action.}
\label{fig:explorer_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{function_example}
\caption{Example of the \textit{function information} functionality of the proposed tool in action.}
\label{fig:function_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{relatory_example}
\caption{Example of the \textit{duplication relatory} functionality X of the proposed tool in action.}
\label{fig:relatory_ex}
\end{figure}
